Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-06 paper/paper.Rmd
delete superfluous to
add notes on CAST

Leave-Location-and-Time-Out (LLTO) from package \pkg{CAST} is a spatiotemporal resampling method [@meyer2018].
It requires both a spatial and a temporal variable which are used to to separate observations in a multi-dimensional space.
It comes with satellite methods named "Leave-time-out" (LTO) and "Leave-location-out" (LLO) which only operate in a two-dimensional space.

@@

The following code uses the `cookfarm` dataset as the base, modifies to the `Date` variable to contain five unique levels and then creates a spatiotemporal regression task in \pkg{mlr3spatiotempcv} (Fig. \@ref(fig:lto)).

@@

```{r llto, echo=FALSE, out.width="70%", fig.cap="Three-dimensional visualization of method 'sptcv\\_cstf' and sub-method 'Leave-Location-And-Time-Out' (LLTO). The grey points show the points omitted by this method, i.e. the points which are not used in the training or test set in this fold.", fig.pos="ht"}
knitr::include_graphics("llto.png")
```

>>>>

Leave-Location-and-Time-Out (LLTO) from package \pkg{CAST} is a spatiotemporal resampling method [@meyer2018].
It requires both a spatial and a temporal variable which are used to separate observations in a multi-dimensional space.
It comes with satellite methods named "Leave-time-out" (LTO) and "Leave-location-out" (LLO) which only operate in a two-dimensional space.

@@

The following code uses the `cookfarm` dataset as the base, modifies the `Date` variable in such a way that it contains five unique levels and then creates a spatiotemporal regression task in \pkg{mlr3spatiotempcv} (Fig. \@ref(fig:lto)).

@@

```{r llto, echo=FALSE, out.width="70%", fig.cap="Three-dimensional visualization of method 'sptcv\\_cstf' and sub-method 'Leave-Location-And-Time-Out' (LLTO). The grey points show the points omitted by this method, i.e. the points which are neither used in the training nor test set in this fold.", fig.pos="ht"}
knitr::include_graphics("llto.png")
```
